### 2023-01-23 Paper/Paper.Rmd
Update 23 Jan

@@

```{r CumRet,  warning =  FALSE, fig.align = 'center', fig.cap = "Cumulative Returns per Sector for ALSI and SWIX \\label{CumRet}", fig.ext = 'png', fig.height = 3, fig.width = 6}

@@

# Now we can use multf to estimate the dcc model using our
# dcc.spec:
fit.dcc = dccfit(spec.dcc, data = xts_swix_return, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf)
fit.dcc_ls = dccfit(spec.dcc_ls, data = xts_swix_return_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_ls)
fit.dcc_nls = dccfit(spec.dcc_nls, data = xts_swix_return_no_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_nls)

# And that is our DCC fitted model!

# We can now test the model's fit as follows: Let's use the
# covariance matrices to test the adequacy of MV model in
# fitting mean residual processes:
RcovList <- rcov(fit.dcc)  # This is now a list of the monthly covariances of our DCC model series.
RcovList_ls <- rcov(fit.dcc_ls)
RcovList_nls <- rcov(fit.dcc_nls)

@@

```{r ALSI, warning =  FALSE, fig.align = 'center', fig.cap = "ALSI Weight Contribution \\label{ALSI}", fig.height = 3, fig.width = 6, dev = 'png'}
weights_plot(T40, "ALSI")
```

```{r SWIX, warning =  FALSE, fig.align = 'center', fig.cap = "SWIX Weight Contribution \\label{SWIX}", fig.height = 3, fig.width = 6, dev = 'png'}
weights_plot(T40, "SWIX")
```

```{r LogRet,  warning =  FALSE, fig.align = 'center', fig.cap = "Log Returns per Sector for the SWIX \\label{LogRet}", fig.ext = 'png', fig.height = 3, fig.width = 6}

@@

```{r DCCfullr,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Resources \\label{DCCfullr}", fig.ext = 'png', fig.height = 3, fig.width = 6}

@@

```{r DCCfullf,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Financials \\label{DCCfullf}", fig.ext = 'png', fig.height = 3, fig.width = 6}

@@

```{r DCCfulli,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Industrials \\label{DCCfulli}", fig.ext = 'png', fig.height = 3, fig.width = 6}

>>>>

```{r eval=FALSE, include=FALSE}
# Alsi_returns <- read_rds("/Users/svenwellmann/Downloads/Alsi_Returns.rds")
# Alsi_returns %>% pull(date) %>% max
```

@@

```{r CumRet,  warning =  FALSE, fig.align = 'center', fig.cap = "Cumulative Returns per Sector for ALSI and SWIX \\label{CumRet}", fig.ext = 'png', fig.height = 4, fig.width = 7}

@@

RcovList <- rcov(fit.dcc)  # This is now a list of the monthly covariances of our DCC model series.
RcovList_ls <- rcov(fit.dcc_ls)
RcovList_nls <- rcov(fit.dcc_nls)

@@

```{r ALSI, warning =  FALSE, fig.align = 'center', fig.cap = "ALSI Weight Contribution \\label{ALSI}", fig.height = 4, fig.width = 7, dev = 'png'}
weights_plot(T40, "ALSI")
```

```{r SWIX, warning =  FALSE, fig.align = 'center', fig.cap = "SWIX Weight Contribution \\label{SWIX}", fig.height = 4, fig.width = 7, dev = 'png'}
weights_plot(T40, "SWIX")
```

```{r LogRet,  warning =  FALSE, fig.align = 'center', fig.cap = "Log Returns per Sector for the SWIX \\label{LogRet}", fig.ext = 'png', fig.height = 4, fig.width = 7}

@@

```{r DCCfullr,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Resources \\label{DCCfullr}", fig.ext = 'png', fig.height = 4, fig.width = 7}

@@

```{r DCCfullf,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Financials \\label{DCCfullf}", fig.ext = 'png', fig.height = 4, fig.width = 7}

@@

```{r DCCfulli,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Industrials \\label{DCCfulli}", fig.ext = 'png', fig.height = 4, fig.width = 7}

### 2023-01-23 Paper/Paper.tex
Update 23 Jan

{[}Resources{]}.omega 0.00000 0.00001 0.304 0.761\\
{[}Resources{]}.alpha1 0.005 0.033 0.147 0.883\\
{[}Resources{]}.beta1 0.947 0.050 18.750 0\\
{[}Industrials{]}.omega 0.00000 0.00000 1.755 0.079\\
{[}Industrials{]}.alpha1 0.017 0.009 1.822 0.068\\
{[}Industrials{]}.beta1 0.907 0.017 54.781 0\\
{[}Financials{]}.omega 0.00000 0.00000 0.966 0.334\\
{[}Financials{]}.alpha1 0.032 0.022 1.492 0.136\\
{[}Financials{]}.beta1 0.907 0.033 27.601 0\\
{[}Joint{]}dcca1 0.039 0.005 7.807 0\\
{[}Joint{]}dccb1 0.949 0.008 123.286 0\\
------------------------------------------------------------

@@

{[}Resources{]}.omega 0.00004 0.00003 1.399 0.162\\
{[}Resources{]}.alpha1 0.00000 0.101 0.00000 1.000\\
{[}Resources{]}.beta1 0.791 0.161 4.907 0.00000\\
{[}Industrials{]}.omega 0.00001 0.00000 24.162 0\\
{[}Industrials{]}.alpha1 0.00000 0.028 0.00000 1.000\\
{[}Industrials{]}.beta1 0.825 0.023 35.958 0\\
{[}Financials{]}.omega 0.00003 0.00001 3.121 0.002\\
{[}Financials{]}.alpha1 0.018 0.058 0.306 0.760\\
{[}Financials{]}.beta1 0.672 0.071 9.408 0\\
{[}Joint{]}dcca1 0.050 0.015 3.414 0.001\\
{[}Joint{]}dccb1 0.895 0.032 27.579 0\\
------------------------------------------------------------

@@

{[}Resources{]}.omega 0.00000 0.00000 0.437 0.662\\
{[}Resources{]}.alpha1 0.026 0.021 1.256 0.209\\
{[}Resources{]}.beta1 0.934 0.035 26.758 0\\
{[}Industrials{]}.omega 0.00000 0.00001 0.365 0.715\\
{[}Industrials{]}.alpha1 0.023 0.036 0.641 0.521\\
{[}Industrials{]}.beta1 0.912 0.074 12.253 0\\
{[}Financials{]}.omega 0.00000 0.00001 0.369 0.712\\
{[}Financials{]}.alpha1 0.039 0.051 0.771 0.441\\
{[}Financials{]}.beta1 0.908 0.075 12.101 0\\
{[}Joint{]}dcca1 0.036 0.005 6.747 0\\
{[}Joint{]}dccb1 0.954 0.008 120.623 0\\
------------------------------------------------------------

>>>>

{[}Resources{]}.omega 0.00000 0.00001 0.304 0.761\\
{[}Resources{]}.alpha1 0.005 0.033 0.147 0.883\\
{[}Resources{]}.beta1 0.947 0.050 18.749 0\\
{[}Industrials{]}.omega 0.00000 0.00000 1.755 0.079\\
{[}Industrials{]}.alpha1 0.017 0.009 1.822 0.068\\
{[}Industrials{]}.beta1 0.907 0.017 54.780 0\\
{[}Financials{]}.omega 0.00000 0.00000 0.966 0.334\\
{[}Financials{]}.alpha1 0.032 0.022 1.492 0.136\\
{[}Financials{]}.beta1 0.907 0.033 27.601 0\\
{[}Joint{]}dcca1 0.039 0.005 7.806 0\\
{[}Joint{]}dccb1 0.949 0.008 123.261 0\\
------------------------------------------------------------

@@

{[}Resources{]}.omega 0.00004 0.00003 1.399 0.162\\
{[}Resources{]}.alpha1 0.00000 0.101 0.00000 1.000\\
{[}Resources{]}.beta1 0.791 0.161 4.907 0.00000\\
{[}Industrials{]}.omega 0.00001 0.00000 24.162 0\\
{[}Industrials{]}.alpha1 0.00000 0.028 0.00000 1.000\\
{[}Industrials{]}.beta1 0.825 0.023 35.958 0\\
{[}Financials{]}.omega 0.00003 0.00001 3.121 0.002\\
{[}Financials{]}.alpha1 0.018 0.058 0.306 0.760\\
{[}Financials{]}.beta1 0.672 0.071 9.408 0\\
{[}Joint{]}dcca1 0.050 0.015 3.414 0.001\\
{[}Joint{]}dccb1 0.895 0.032 27.577 0\\
------------------------------------------------------------

@@

{[}Resources{]}.omega 0.00000 0.00000 0.437 0.662\\
{[}Resources{]}.alpha1 0.026 0.021 1.256 0.209\\
{[}Resources{]}.beta1 0.934 0.035 26.758 0\\
{[}Industrials{]}.omega 0.00000 0.00001 0.365 0.715\\
{[}Industrials{]}.alpha1 0.023 0.036 0.641 0.521\\
{[}Industrials{]}.beta1 0.912 0.074 12.253 0\\
{[}Financials{]}.omega 0.00000 0.00001 0.369 0.712\\
{[}Financials{]}.alpha1 0.039 0.051 0.771 0.441\\
{[}Financials{]}.beta1 0.908 0.075 12.101 0\\
{[}Joint{]}dcca1 0.036 0.005 6.747 0\\
{[}Joint{]}dccb1 0.954 0.008 120.629 0\\
------------------------------------------------------------

### 2023-01-23 README.rmd
Update 23 Jan

# Now we can use multf to estimate the dcc model using our
# dcc.spec:
fit.dcc = dccfit(spec.dcc, data = xts_swix_return, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf)
fit.dcc_ls = dccfit(spec.dcc_ls, data = xts_swix_return_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_ls)
fit.dcc_nls = dccfit(spec.dcc_nls, data = xts_swix_return_no_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_nls)

>>>>

# Now we can use multf to estimate the dcc model using our
# dcc.spec:
#fit.dcc = dccfit(spec.dcc, data = xts_swix_return, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf)
#fit.dcc_ls = dccfit(spec.dcc_ls, data = xts_swix_return_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_ls)
#fit.dcc_nls = dccfit(spec.dcc_nls, data = xts_swix_return_no_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_nls)

#saveRDS(fit.dcc, file = "fit.dcc.rds")
#saveRDS(fit.dcc_ls, file = "fit.dcc_ls.rds")
#saveRDS(fit.dcc_nls, file = "fit.dcc_nls.rds")

# I have saved and read in the files to help save knitting time

fit.dcc = readRDS(file = "fit.dcc.rds")
fit.dcc_ls = readRDS(file = "fit.dcc_ls.rds")
fit.dcc_nls = readRDS(file = "fit.dcc_nls.rds")
